### 2017-05-13 paper/evaluation.tex
spell checking

Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

@@

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can ocurr when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.

@@

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites are modularized and
those modules are tested independetly in CI servers through different
parameters.  Those participants argumented that such practice helps to
reduce time to observe test failures, which is the goal of speeding up
regression testing.  A total of \emailsLocal{} participants answered
that they do run tests in their local machines.  Note, however, that
CI does not preclude low-level parallelization.  For example,
installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
in dedicated servers would benefit from running tests faster through
low-level test suite parallelization.

@@

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the particpant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQAdoptionOne{}).

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  Three
cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
\CodeIn{Log4J2}.  No significant speedup was observed in
\CodeIn{Chaos}, a project with only three test classes, of which one
monopolizes the bulk of test execution time.  This project uses
configuration \ParClassSeqMeth{}, which runs test classes in parallel
and test methods, declared in each class, sequentially.  Consequently,
speedup cannot be obtained as the cost of the single expensive test
class cannot be broken down with the selected configuration.  Although
project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
results obtained are very different compared to \CodeIn{Chaos}.  The
speedup observed in \CodeIn{Jcabi} was the highest amongst all
projects.  This project contains test classes with a small number of
test methods and several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.  Finally, we note that parallel
execution in \CodeIn{Log4J2} was innefective.  We found that Maven
invokes several test modules in this project but the test modules that
dominate execution time run sequentially by default.

@@

It is worth mentioning that we used JUnit as opposed to Maven to run
configurations \emph{C*}.  After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \emph{C*}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
nonsignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall tha deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated outputed from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs

>>>>

Figure~\ref{tab:freqmodes-dynamic} shows the projects we identified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

@@

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.

@@

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDiistributed{} of
these participants reporting that test suites are modularized and
those modules are tested independently in CI servers through different
parameters.  Those participants explained that such practice helps to
reduce time to observe test failures, which is the goal of speeding up
regression testing.  A total of \emailsLocal{} participants answered
that they do run tests in their local machines.  Note, however, that
CI does not preclude low-level parallelization.  For example,
installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
in dedicated servers would benefit from running tests faster through
low-level test suite parallelization.

@@

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the participant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQAdoptionOne{}).

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  Three
cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
\CodeIn{Log4J2}.  No significant speedup was observed in
\CodeIn{Chaos}, a project with only three test classes, of which one
monopolizes the bulk of test execution time.  This project uses
configuration \ParClassSeqMeth{}, which runs test classes in parallel
and test methods, declared in each class, sequentially.  Consequently,
speedup cannot be obtained as the cost of the single expensive test
class cannot be broken down with the selected configuration.  Although
project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
results obtained are very different compared to \CodeIn{Chaos}.  The
speedup observed in \CodeIn{Jcabi} was the highest amongst all
projects.  This project contains test classes with a small number of
test methods and several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.  Finally, we note that parallel
execution in \CodeIn{Log4J2} was ineffective.  We found that Maven
invokes several test modules in this project but the test modules that
dominate execution time run sequentially by default.

@@

It is worth mentioning that we used JUnit as opposed to Maven to run
configurations \emph{C*}.  After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \emph{C*}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we invoke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
insignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall that deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock
%%  LocalWords:  mapdb workflow XPath
